Democracy, Public Support, and Measurement Uncertainty

### 2021-05-12 paper/dcpo_demsupport.Rmd
version with all the models

```{r dcpoPointAJPS, eval = TRUE}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=8}

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
load(here::here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

@@

```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=5}

load(here::here("output", "estimates_clsMeanAPSR.RDS"))
load(here::here("output", "estimates_clsAPSR.RDS"))
load(here::here("output", "estimates_dcpoAPSR.RDS"))

df_plot <- df_result_clsAPSR[[1]] %>% 
  mutate(model = "Claassen 2020b")

df_plot <- df_result_clsUncertainAPSR[[1]] %>% 
  mutate(model = "Claassen w/ Uncertainty") %>%  
  bind_rows(df_plot)

df_plot <- df_result_dcpoAPSR[[1]] %>% 
  mutate(model = "DCPO") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)"),
    time = 3)
  )

terms <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Liberal~democracy",
                      "Liberal~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Liberal~democracy",
                               "Liberal~democracy[t-1]",
                               "Delta~Log~GDP~per~capita",
                               "Log~GDP[t-1]")))

df_tableAPSR <- df_plotS %>% mutate(
  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
  group = "Basic"
) %>% 
  select(term, estimate, conf, n, model, group) %>% 
  fill(n, .direction = "up")

plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Public Support for Democracy",
    subtitle = "Basic"
  ) +
  theme(legend.position = "none")

df_plot <- df_result_clsAPSR[[2]] %>% 
  mutate(model = "Claassen 2020b")

df_plot <- df_result_clsUncertainAPSR[[2]] %>% 
  mutate(model = "Claassen w/ Uncertainty") %>%  
  bind_rows(df_plot)

df_plot <- df_result_dcpoAPSR[[2]] %>% 
  mutate(model = "DCPO") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democratic\n Mood\n (t-1)",
        "Democratic\n Mood\n (t-2)",
      "Liberal\n Democracy\n (Difference)",
      "Liberal\n Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)",
      "Corruption\n (Difference)",
      "Corruption\n (t-1)"
      ),time = 3)
  )

@@

df_tableAPSR <- df_plotS %>% mutate(
  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
  group = "W. Corruption"
) %>% 
  select(term, estimate, conf, n, model, group) %>% 
  fill(n, .direction = "up") %>% 
  bind_rows(df_tableAPSR) %>% 
  mutate(estimate = round(estimate, digits = 3))

plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "w/ Corruption"
  ) +
  theme(legend.position = "bottom", legend.title = element_blank())

legend <- get_legend(plot_APSR2)

plot_APSR2 <- plot_APSR2 +
  theme(legend.position = "none")

gridExtra::grid.arrange(plot_APSR1, plot_APSR2, legend, ncol=2, nrow = 2, 
             layout_matrix = rbind(c(1,2), c(3,3)),
             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
```

@@

```{r save_tables, eval=TRUE}
save(df_tableAJPS, df_tableAPSR, file = here::here("output", "df_tables.rda"))

@@

```{r num-cls2020b, results='asis', eval = TRUE}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)

modelsummary(ls_mods, 
             stars = TRUE,
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

>>>>

```{r dcpoPointAJPS}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

@@

```{r visualizedAPSR, fig.cap= "\\label{fig:visualizedAPSR} The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

load(here::here("output", "estimates_clsMeanAPSR.RDS"))
load(here::here("output", "estimates_clsAPSR.RDS"))
result_dcpoAPSR <- readRDS(here::here("output", "estimates_dcpoAPSR.RDS"))

# Regime compacted ####

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$pooled1[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$fd1[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)"),
    time = 3),
    rep(
      c("Liberal Democracy\n (Difference)", 
        "Log GDP\n per capita\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms1 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Liberal~democracy",
                      "Liberal~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Liberal~democracy",
                               "Liberal~democracy[t-1]",
                               "Delta~Log~GDP~per~capita",
                               "Log~GDP[t-1]")))

plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms1))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Public Support for Democracy",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$pooled2[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$fd2[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)",
      "Corruption\n (Difference)",
      "Corruption\n (t-1)"
      ),
    time = 3),
    rep(
      c("Liberal Democracy\n (Difference)", 
        "Log GDP\n per capita\n (Difference)",
        "Corruption\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

@@

plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "W. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "none")

# Regime specified ####

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$`pooled-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$`fd-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Electoral Democracy\n (Difference)",
      "Electoral Democracy\n (t-1)",
      "Minoritarian Democracy\n (Difference)",
      "Minoritarian Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)"),
    time = 3),
    rep(
      c("Electoral Democracy\n (Difference)", 
        "Minoritarian Democracy\n (Difference)",
        "Log GDP\n per capita\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms3 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")),
                levels = rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")))

plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$`pooled-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoAPSR$`fd-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Electoral Democracy\n (Difference)",
      "Electoral Democracy\n (t-1)",
      "Minoritarian Democracy\n (Difference)",
      "Minoritarian Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)",
      "Corruption\n (Difference)",
      "Corruption\n (t-1)"
      ),
    time = 3),
    rep(
      c("Electoral Democracy\n (Difference)", 
        "Minoritarian Democracy\n (Difference)",
        "Log GDP\n per capita\n (Difference)",
        "Corruption\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms4 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP",
                      "Log~GDP[t-1]",
                      "Delta~Corruption",
                      "Corruption[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Electoral~democracy",
                               "Electoral~democracy[t-1]",
                               "Delta~Minoritarian~democracy",
                               "Minoritarian~democracy[t-1]",
                               "Delta~Log~GDP",
                               "Log~GDP[t-1]",
                               "Delta~Corruption",
                               "Corruption[t-1]")))

plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms4))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified w. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

legend <- get_legend(plot_RegAPSR2)

plot_RegAPSR2 <- plot_RegAPSR2 + theme(legend.position = "none")

grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
```

@@

@@

```{r num-cls2020b, results='asis', eval = TRUE}
tb_result_clsAPSR <- map(result_clsAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM w. Corruption", "ECM w. Corruption-Regime", "FD w. Corruption", "FD w. Corruption-Regime")

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)

modelsummary(tb_result_clsAPSR, 
             stars = TRUE,
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-cls2020bUncertain, results='asis', eval = TRUE}
tb_result_clsUncertainAPSR <- map(result_clsUncertainAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_clsUncertainAPSR) <- c("ECM", "ECM-Regime", 
                          "FD", "FD-Regime", 
                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
                          "FD w. Corruption", "FD w. Corruption-Regime")

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)

modelsummary(tb_result_clsUncertainAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-cls2020bDCPO, results='asis', eval = TRUE}
tb_result_dcpoAPSR <- map(result_dcpoAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_dcpoAPSR) <- c("ECM", "ECM-Regime", 
                          "FD", "FD-Regime", 
                          "ECM w. Corruption", "ECM w. Corruption-Regime", 
                          "FD w. Corruption", "FD w. Corruption-Regime")

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(theta, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(theta, 1:2)2" = "Democratic\n Mood\n (t-2)",

  "diff(Vdem_libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Vdem_libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Vdem_libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",

  "diff(Vdem_polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Vdem_polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Vdem_polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Vdem_liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Vdem_liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Vdem_liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lg_imp_mdpgdp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lg_imp_mdpgdp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lg_imp_mdpgdp, 1)" = "Log GDP\n (t-1)",
  "diff(corruption_z, lag = 1)" = "Corruption\n (Difference)",
  "corruption_z" = "Corruption\n (Difference)",
  "plm::lag(corruption_z, 1)" = "Corruption\n (t-1)"
)

modelsummary(tb_result_dcpoAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```
